Estimating individual subjective values of emotion regulation strategies

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}, figures S1 to S7 and table S2 to S8.

@@

To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.

@@

@@

\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}

ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 1, 15 & 3895.91 & 34.32 *** & .475 & <.001\\
\hline
\end{tabular}

\(BF10=\) 1,244.99

Paired contrasts:

@@

\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{neutral} - View_{negative}$ & -129.28 & 22.07 & 15.00 & -5.86 & 0.00 & 794.78 & 0.70 & {}[0.43, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

@@

Figure:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjArousalViewPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots. Each dot represents the arousal rating of a single subject. Bold dots represent outliers.}\label{fig:FigSubjArousalViewPilot}
\end{figure}

\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}

ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 2.79, 41.89 & 2238.27 & 1.17 & .011 & .332\\
\hline
\end{tabular}

\(BF10=\) 0.11

Paired contrasts:

@@

\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & -0.74 & 16.14 & 45.00 & -0.05 & 1.00 & 0.26 & 4.68e-05 & {}[0.00, 1.00]\\
$View_{negative} - Distancing$ & -5.35 & 16.14 & 45.00 & -0.33 & 1.00 & 0.27 & 2.43e-03 & {}[0.00, 1.00]\\
$View_{negative} - Suppression$ & -26.23 & 16.14 & 45.00 & -1.63 & 0.67 & 1.25 & 0.06 & {}[0.00, 1.00]\\
$Distraction - Distancing$ & -4.61 & 16.14 & 45.00 & -0.29 & 1.00 & 0.26 & 1.81e-03 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & -25.49 & 16.14 & 45.00 & -1.58 & 0.73 & 0.77 & 0.05 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & -20.88 & 16.14 & 45.00 & -1.29 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

@@

Figure:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjArousalRegPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots. Each dot represents the arousal rating of a single subject. Bold dots represent outliers.}\label{fig:FigSubjArousalRegPilot}
\end{figure}

\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}

\emph{Corrugator}: ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 1, 15 & 1.01 & 9.70 ** & .237 & .007\\
\hline
\end{tabular}

\(BF10=\) 6,690,401.91

Paired contrasts:

@@

\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{neutral} - View_{negative}$ & -1.11 & 0.36 & 15.00 & -3.11 & 0.01 & 5,019,313.20 & 0.39 & {}[0.09, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

@@

\emph{Levator}: ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 1, 15 & 0.17 & 7.72 * & .162 & .014\\
\hline
\end{tabular}

\(BF10=\) 48.44

Paired contrasts:

@@

\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{neutral} - View_{negative}$ & -0.40 & 0.14 & 15.00 & -2.78 & 0.01 & 41.02 & 0.34 & {}[0.05, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

@@

Figures:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGCorrViewPilot-1} \caption{Corrugator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.}\label{fig:FigEMGCorrViewPilot}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGLevViewPilot-1} \caption{Levator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.}\label{fig:FigEMGLevViewPilot}
\end{figure}

\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}

\emph{Corrugator}: ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 1.53, 22.98 & 1.16 & 5.71 * & .189 & .015\\
\hline
\end{tabular}

\(BF10=\) 5,257,689.54

Paired contrasts:

@@

\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 4,962.89 & 0.19 & {}[0.05, 1.00]\\
$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 616.63 & 0.21 & {}[0.06, 1.00]\\
$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 11,678.82 & 0.20 & {}[0.06, 1.00]\\
$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 0.07 & 1.78e-03 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 0.08 & 7.22e-04 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 0.06 & 2.36e-04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

@@

\emph{Levator}: ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 2.07, 31.00 & 0.20 & 8.27 ** & .225 & .001\\
\hline
\end{tabular}

\(BF10=\) 672,341.29

Paired contrasts:

\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & 0.42 & 0.13 & 45.00 & 3.24 & 0.01 & 58.02 & 0.19 & {}[0.05, 1.00]\\
$View_{negative} - Distancing$ & 0.45 & 0.13 & 45.00 & 3.46 & 0.01 & 93.49 & 0.21 & {}[0.06, 1.00]\\
$View_{negative} - Suppression$ & 0.62 & 0.13 & 45.00 & 4.79 & 0.00 & 6,253.91 & 0.34 & {}[0.16, 1.00]\\
$Distraction - Distancing$ & 0.03 & 0.13 & 45.00 & 0.22 & 1.00 & 0.07 & 1.06e-03 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & 0.20 & 0.13 & 45.00 & 1.54 & 0.78 & 1.52 & 0.05 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 0.17 & 0.13 & 45.00 & 1.32 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

Figures:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGCorrRegPilot-1} \caption{Corrugator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.}\label{fig:FigEMGCorrRegPilot}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGLevRegPilot-1} \caption{Levator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.}\label{fig:FigEMGLevRegPilot}
\end{figure}

\hypertarget{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
\subsection{Pilot study: Subjective effort in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}

ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 2.38, 35.66 & 4388.19 & 11.13 *** & .185 & <.001\\
\hline
\end{tabular}

\(BF10=\) 7.40

Paired contrasts:

\caption{\label{tab:unnamed-chunk-10}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
$View_{negative} - Distancing$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
$View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\
$Distraction - Distancing$ & 21.00 & 20.85 & 45.00 & 1.01 & 1.00 & 0.50 & 0.02 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.57 & 0.03 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 0.26 & 1.27e-04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

Figure:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjEffortPilot-1} \caption{Subjective effort ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.}\label{fig:FigSubjEffortPilot}
\end{figure}

>>>>

The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the OSF repository (\url{https://osf.io/vnj8x/}).

@@

To investigate whether individual SVs predict ER choice (H7a), a \(\chi{2}\) test with predicted choice (highest SV of each participant) and actual choice was computed.
Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.

@@

\hypertarget{manipulation-checks}{%
\subsubsection{Manipulation checks}\label{manipulation-checks}}

\hypertarget{subjective-arousal-and-physiological-responding}{%
\paragraph{Subjective arousal and physiological responding}\label{subjective-arousal-and-physiological-responding}}

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator}, and \emph{Levator} activity.
We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\)´, \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator}, and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see \protect\hyperlink{SupplementEffectER}{supplementary material}.

\hypertarget{subjective-effort-of-er-strategies}{%
\paragraph{Subjective effort of ER strategies}\label{subjective-effort-of-er-strategies}}

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\)).
Post-hoc test showed significant higher subjective effort for distraction (\(\eta_{p}^{2}=0.47, [0.42, 1.00]\), \(BF_{10}=\) \(3.61 \times 10^{30}\)), distancing (\(\eta_{p}^{2}=0.41, [0.35, 1.00]\), \(BF_{10}=\) \(1.60 \times 10^{28}\)), and suppression (\(\eta_{p}^{2}=0.30, [0.23, 1.00]\), \(BF_{10}=\) \(1.27 \times 10^{19}\)) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\) \(1.61 \times 10^{6}\)) and distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\) 29.19).

\hypertarget{subjective-values-of-er-strategies}{%
\paragraph{Subjective values of ER strategies}\label{subjective-values-of-er-strategies}}

{[}to be filled{]}

\hypertarget{associations-between-subjective-values-and-flexible-er}{%
\paragraph{Associations between subjective values and flexible ER}\label{associations-between-subjective-values-and-flexible-er}}

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).

{[} HIER FEHLT NOCH DIE ORDINALE REGRESSION {]}

Last, we investigated whether SVs are associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
We found neither a significant associations between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).

@@

\hypertarget{SupplementNV}{%
\subsection{Test for normal distribution of predictor variables}\label{SupplementNV}}

@@

\caption{\label{tab:TabNV}Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{$W$} & \multicolumn{1}{c}{$p$}\\
\midrule
Arousal View Neu & 26.63 & 39.12 & 0.68 & 0.00\\
Arousal View Neg & 187.78 & 87.31 & 0.98 & 0.06\\
Arousal Distraction & 158.13 & 92.49 & 0.97 & 0.01\\
Arousal Distancing & 168.62 & 95.75 & 0.98 & 0.04\\
Arousal Suppression & 163.96 & 87.17 & 0.98 & 0.07\\
Effort View Neu & 18.15 & 27.37 & 0.65 & 0.00\\
Effort View Neg & 49.40 & 62.26 & 0.74 & 0.00\\
Effort Distraction & 208.46 & 96.15 & 0.98 & 0.13\\
Effort Distancing & 158.26 & 99.50 & 0.97 & 0.01\\
Effort Suppression & 189.80 & 92.34 & 0.98 & 0.12\\
\bottomrule
\end{tabular}

@@

@@

\caption{\label{tab:TabNV}Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{$W$} & \multicolumn{1}{c}{$p$}\\
\midrule
Corrgator View Neu & 0.04 & 6.99 & 0.05 & 0.00\\
Corrgator View Neg & 1.03 & 7.21 & 0.19 & 0.00\\
Corrgator Distraction & 0.00 & 7.67 & 0.04 & 0.00\\
Corrgator Distancing & 0.07 & 3.78 & 0.08 & 0.00\\
Corrgator Suppression & 0.25 & 1.92 & 0.35 & 0.00\\
Levator View Neu & 0.09 & 1.84 & 0.38 & 0.00\\
Levator View Neg & 0.58 & 3.20 & 0.43 & 0.00\\
Levator Distraction & -0.05 & 1.16 & 0.52 & 0.00\\
Levator Distancing & -0.03 & 0.92 & 0.48 & 0.00\\
Levator Suppression & 0.01 & 1.00 & 0.55 & 0.00\\
\bottomrule
\end{tabular}

@@

\hypertarget{SupplementEffectER}{%
\subsection{Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding}\label{SupplementEffectER}}

@@

\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on subjective arousal ratings.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & 29.65 & 6.68 & 357.00 & 4.44 & 0.00 & 168.48 & 0.05 & {}[0.02, 1.00]\\
$View_{negative} - Distancing$ & 23.82 & 6.68 & 357.00 & 3.57 & 0.00 & 62.99 & 0.03 & {}[0.01, 1.00]\\
$View_{negative} - Suppression$ & 19.16 & 6.68 & 357.00 & 2.87 & 0.03 & 1.97 & 0.02 & {}[0.00, 1.00]\\
$Distraction - Distancing$ & -5.83 & 6.68 & 357.00 & -0.87 & 1.00 & 0.18 & 2.13e-03 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & -10.49 & 6.68 & 357.00 & -1.57 & 0.70 & 0.31 & 6.86e-03 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & -4.66 & 6.68 & 357.00 & -0.70 & 1.00 & 0.14 & 1.36e-03 & {}[0.00, 1.00]\\
\bottomrule
\end{tabular}

@@

@@

\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Corrugator activity}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & 0.18 & 0.04 & 351.00 & 4.79 & 0.00 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
$View_{negative} - Distancing$ & 0.19 & 0.04 & 351.00 & 5.09 & 0.00 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
$View_{negative} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & 18,426,055.49 & 0.08 & {}[0.04, 1.00]\\
$Distraction - Distancing$ & 0.01 & 0.04 & 351.00 & 0.30 & 1.00 & 0.04 & 2.61e-04 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & 0.03 & 0.04 & 351.00 & 0.88 & 1.00 & 0.08 & 2.21e-03 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 0.02 & 0.04 & 351.00 & 0.58 & 1.00 & 0.05 & 9.51e-04 & {}[0.00, 1.00]\\
\bottomrule
\end{tabular}

@@

@@

\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Levator activity}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & 202,428,623,285.88 & 0.11 & {}[0.07, 1.00]\\
$View_{negative} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & 39,887,367.63 & 0.08 & {}[0.04, 1.00]\\
$View_{negative} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & 86,036,487,908.69 & 0.10 & {}[0.06, 1.00]\\
$Distraction - Distancing$ & -0.05 & 0.05 & 351.00 & -1.07 & 1.00 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & -0.02 & 0.05 & 351.00 & -0.36 & 1.00 & 0.04 & 3.70e-04 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 0.04 & 0.05 & 351.00 & 0.71 & 1.00 & 0.10 & 1.44e-03 & {}[0.00, 1.00]\\
\bottomrule
\end{tabular}

@@
